The Chemistry Development Kit (CDK) \cdkversion{}: atom typing, depiction, molecular formulas, and substructure searching

### 2017-04-27 article.tex

  The perception from coordinates and wedge assignment algorithms are fundamental for conversion
  between formats that store stereochemistry implicitly based on coordinates (e.g. molfile\footnote{Molfiles 
  can also store tetrahedral stereochemistry as a parity value, this is read if no coordinates are specified.
  In general there is no guarantee the parity value is read and the only portable way to store
  stereochemistry in a molfile is with coordinates.}, CML) and 
  explicitly (e.g. SMILES, CML, InChI). Perception from 2D coordinates 
  can optionally identify
  perspective projections, specifically: Fischer, Haworth, and Chair projections. With the perception of 
  perspective projections enabled, database entries currently considered distinct can be merged
  (Figure~\ref{fig:stereoprojections}).  The perception from projections is based on an  algorithm briefly  
  described by~\cite{Karapetyan2015}. Other aspects of stereochemistry handling
  are detailed thoroughly in Chapter 6 of ~\cite{May2015}.

@@

  Graph matching of stereochemistry with the described representation is straight forward. Given
  the atom-atom mapping from a query structure to a target molecule, the focus and carriers of 
  the query stereochemistry are mapped to the target. Using the permutation parity of this mapping
  the configurations were compared. SMARTS matching requires some special handling for complex cases 
  \cite{May2014_SMARTS}. For canonicalization, a partial canonical ordering is used to assign an 
  absolute label which can then be integrated into the ordering. More detailed descriptions of 
  these algorithms are described in detail in Chapter~6 of~\cite{May2015}.

>>>>

  The perception from coordinates and wedge assignment algorithms are fundamental for conversion
  between formats that store stereochemistry implicitly based on coordinates (e.g. molfile\footnote{Molfiles 
  can also store tetrahedral stereochemistry as a parity value, this is read if no coordinates are specified.
  In general there is no guarantee the parity value is read and the only portable way to store
  stereochemistry in a molfile is with coordinates.}, CML) and 
  explicitly (e.g. SMILES, CML, InChI). Perception from 2D coordinates 
  can optionally identify
  perspective projections, specifically: Fischer, Haworth, and Chair projections. With the perception of 
  perspective projections enabled, database entries currently considered distinct can be merged
  (Figure~\ref{fig:stereoprojections}).

@@

  Pattern matching of stereochemistry with the described representation is straight forward. Given
  the atom-atom mapping from a query structure to a target molecule, the focus and carriers of 
  the query stereochemistry are mapped to the target. Using the permutation parity of this mapping
  the configurations were compared. SMARTS matching requires some special handling for complex cases 
  \cite{May2014_SMARTS}. For canonicalization, a partial canonical ordering is used to assign an 
  absolute label which can then be integrated into the ordering. The algorithms used
  for stereochemistry are thoroughly detailed in Chapter~6 of~\cite{May2015}. The perception
  from projections is based on an algorithm briefly described by~\cite{Karapetyan2015}.
